Ecological network control

### 2018-04-19 publication/manuscript.Rmd
Read and use network metadata

>>>>

```{r load-metadata}
loadd(metadata)
lop <- filter(metadata, study == "lopezaraiza") %>% mutate(size = n_pla + n_pol) %$% size %>% summary() 
bar <- filter(metadata, study == "bartomeus") %>% mutate(size = n_pla + n_pol) %$% size %>% summary() 
```

We apply methods of control theory to ten paired pollination networks.
Each network pair was composed of a community invaded by a plant and a community free of the invasive species. 
Four pairs were obtained from natural or semi-natural vegetation communities in the city of Bristol, UK [@Lopezaraiza-Mikel2007]. 
These networks are comprised of `r lop[1]`--`r lop[6]` species (mean `r round(lop[4])`), and non-invaded plots were obtained by experimentally removing all the flowers of the invasive species *Impatients grandulifera*.
The other six pairs were obtained from lower diversity Mediterranean shrublands in Cap de Creus National Park, Spain [@Bartomeus2008].
These networks are comprised of `r bar[1]`--`r bar[6]` species (mean `r round(bar[4])`); in contrast to the above, uninvaded communities were obtained from plots that had not yet been colonised by either of the invasive species *Carpobrotus affine acinaciformis* or *Opuntia stricta*.  
Supplementary Information S\@ref(S-empirical-networks)
